---
title: "johns_test"
author: "john houghton"
date: "Friday, January 09, 2015"
output: 
  html_document:
    toc: true
runtime: shiny
---
# Trended Performance with dygraphs()
```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/jh_dygraphs", package="shiny"),
  options=list(
    width="100%", height = 500
  )
)
```


#### Example: Action Report Data Table & Embedded Application

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/jh_text_input", package="shiny"),
  options=list(
    width="100%", height = 200
  )
)
```

# Action Report
```{r, echo = FALSE}
# Enter your action ids here, comma separated
action_ids <- " 20525217,20524903 "
```

**[ Here, I'm invisibly loading a live action_report ]**

```{r, echo=FALSE}
library(RODBC)
conn <- odbcConnect("rfi_meta_data")
action_report_query <- ("SELECT   c.campaign_name AS campaign_name
                        , c.action_name AS action_name
                        , c.conversion_day AS conversion_day
                        , SUM(c.click_through) as click_through
                        , SUM(view_through) as view_through
                        , SUM(c.click_through) + SUM(view_through) AS total_conversions 
                        
                        FROM (   
                          SELECT cav.name AS action_name  
                          , IF(b.campaign_id=0,'alien',c.label) AS campaign_name
                          , b.*
                            FROM  
                          (	
                            SELECT  ca.current_version_id AS current_version_id	
                            , a.click_through + a.view_through AS total_conversions
                            , a.* 
                              FROM rfi_meta_data.rfi_aggregate_conversion_action_agg a	
                            LEFT JOIN rfi_conversion_action ca ON a.conversion_action_id=ca.id
                            WHERE a.conversion_action_id IN (%s) 	
                            AND conversion_day BETWEEN DATE_SUB(NOW(), INTERVAL 90 DAY) AND NOW()
                            #NAME?
                          ) b	
                          LEFT JOIN rfi_conversion_action_version cav ON cav.version_id=b.current_version_id	
                          LEFT JOIN campaign c ON b.campaign_id=c.id	
                        ) c	
                        
                        GROUP BY c.campaign_name	
                        , c.action_name
                        , c.conversion_day
                        ORDER BY conversion_day DESC"	) 
action_report <- sqlQuery(conn, sprintf(action_report_query, action_ids)) 


```

```{r, echo=FALSE}
library(ggplot2)
inputPanel(
  
  selectInput("campaign_name", label = "Alien vs Credited:",
              choices = c("alien","Ski.com Fall. Sep 2014 - Jan 2015"), selected = "alien"),
  
inputPanel(
  selectInput("action_name", label = "Action Name:",
              choices = c(retargeting = "Ski.com - Retargeting Pixel", conversion = "Ski.com - Request a Quote Conversion" ), selected = "Ski.com - Request a Quote Conversion"),  
  
  sliderInput("date_range", label = "Date Range:",
              min = 7, max = 70, value = 28, step = 7)
              )
          )

renderPlot({
  ggplot(subset(action_report,campaign_name == input$campaign_name & conversion_day > Sys.Date()-input$date_range & action_name %in% input$action_name), aes(x = conversion_day, y = total_conversions, colour = action_name)) + stat_smooth(level = 0.99) + geom_point() + xlab(input$campaign_name)
})
```


## Example: Action Report Data Table & Embedded Application

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/jh_datatables_actions", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

# Checklist 
### Margin / Performance Correlation Analysis
##### Ad rejections
##### Model Changes
##### Model Calibration
##### Day of Week Pacing Variance


# Models Summary
#### Changes in models for this campaign
```{r, echo=FALSE}
library(RODBC)
conn <- odbcConnect("rfi_meta_data")
model_change_query <-("
SELECT old_me_conversion as 'models_name'
, old_m_conversion as 'model_ids'
, date(snapshot_date) as 'change_date'
 FROM rfi_analytics.ds_campaign_model_change_history
where campaign_id = 34377;
")
model_change <- sqlQuery(conn,model_change_query) 
model_change

```

***
# Project Outline: Given a campaign_id
* Trended Performance
  + By Line Item
  + By tactic
  + CTR vs CPA
* Action Report
  + Trended by campaign_id, action_name, date_range
  + Data Sheet, to see raw #s with same filter as chart ^
  + Download Report Option
* Day of Week Pacing Variance Analysis
* Model Calibration
* Viewability
* Margin Snapshot
* Attribution Snapshot

